The Galaxy Cluster Merger Catalog: An Online Repository of Mock Observations from Simulated Galaxy Cluster Mergers

### 2016-09-08 paper/ms.tex
Some more text for the paper

The idea behind the catalog is to provide a way to connect simulations of galaxy cluster mergers
with multiwavelength observations of real merging clusters. Producing simulation data in terms of
observed quantities at many different epochs and from many different lines of sight provides an
opportunity for observers to compare clusters in their observations with a particular merging
scenario. The data here may also be analyzed in its own right, to make predictions for what various investigations of real clusters may reveal.

@@

At the time of writing, the catalog contains data products from idealized binary cluster merger
simulations. The types of data products listed here are appropriate for such simulations. In the future, the catalog will include data products from a variety of cluster merger and related simulations, including those from cosmological simulations and simulations of interactions between clusters and their member galaxies. The types of data products are likely to expand and diversify with the inclusion of new simulations.

@@

The data products are all written in the FITS format, in image and table form. Each FITS file may contain more than one image or table extension. The header of each extension contains coordinate information stored using the standard World Coordinate System (WCS) keywords. Each FITS file contains one or both of the following two coordinate systems:

@@

\begin{thebibliography}{}
\bibitem[Br{\"u}ggen et al.(2012)]{bru12} Br{\"u}ggen, M., Bykov, A., Ryu, D., R{\"o}ttgering, H.\ 2012, \ssr, 166, 187
\bibitem[Brunetti \& Lazarian(2007)]{bru07} Brunetti, G., \& Lazarian, A.\ 2007, \mnras, 378, 245
\bibitem[Clowe et al.(2004)]{clo04} Clowe, D., Gonzalez, A., \& Markevitch, M.\ 2004, \apj, 604, 596
\bibitem[Chluba et al.(2012)]{chl12} Chluba, J., Nagai, D., Sazonov, S., \& Nelson, K.\ 2012, \mnras, 426, 510
\bibitem[Chluba et al.(2013)]{chl13} Chluba, J., Switzer, E., Nelson, K., \& Nagai, D.\ 2013, \mnras, 430, 3054
\bibitem[Donnert et al.(2013)]{don13} Donnert, J., Dolag, K., Brunetti, G., \& Cassano, R.\ 2013, \mnras, 429, 3564
\bibitem[Feretti(2005)]{fer05} Feretti, L.\ 2005, Advances in Space Research, 36, 729
\bibitem[Ford et al.(2014)]{for14} Ford, J., Hildebrandt, H., Van Waerbeke, L., et al.\ 2014, \mnras, 439, 3755
\bibitem[Forman et al.(1972)]{for72} Forman, W., Kellogg, E., Gursky, H., Tananbaum, H., \& Giacconi, R.\ 1972, \apj, 178, 309
\bibitem[Markevitch et al.(2004)]{mar04} Markevitch, M., Gonzalez, A.~H., Clowe, D., et al.\ 2004, \apj, 606, 819
\bibitem[Poole et al.(2006)]{poo06} Poole, G.~B., Fardal, M.~A., Babul, A., McCarthy, I.~G., Quinn, T., \& Wadsley, J.\ 2006, \mnras, 373, 881
\bibitem[Ricker \& Sarazin(2001)]{ric01} Ricker, P.~M., \& Sarazin, C.~L.\ 2001, \apj, 561, 621
\bibitem[Skillman et al.(2013)]{ski13} Skillman, S.~W., Xu, H., Hallman, E.~J., et al.\ 2013, \apj, 765, 21
\bibitem[Sunyaev \& Zeldovich(1972)]{sun72} Sunyaev, R.~A., \& Zeldovich, Y.~B.\ 1972, Comments on Astrophysics and Space Physics, 4, 173
\bibitem[Turk et al.(2011)]{tur11} Turk, M.~J., Smith, B.~D., Oishi, J.~S., Skory, S., Skillman, S.~W., Abel, T., \& Norman, M.~L.\ 2011, \apjs, 192, 9
\bibitem[van Weeren et al.(2010)]{vwe10} van Weeren, R.~J., R{\"o}ttgering, H.~J.~A., Br{\"u}ggen, M., \& Hoeft, M.\ 2010, Science, 330, 347
\bibitem[Vazza et al.(2009)]{vaz09} Vazza, F., Brunetti, G., Kritsuk, A., et al.\ 2009, \aap, 504, 33
\bibitem[Yu et al.(2015)]{yu15} Yu, L., Nelson, K., \& Nagai, D.\ 2015, \apj, 807, 12
\bibitem[ZuHone et al.(2010)]{zuh10} ZuHone, J.~A., Markevitch, M., \& Johnson, R.~E.\ 2010, \apj, 717, 908 (ZMJ10)
\bibitem[ZuHone(2011)]{zuh11} ZuHone, J.~A.\ 2011, \apj, 728, 54 (Z11)
\bibitem[ZuHone et al.(2014)]{zuh14} ZuHone, J.~A., Biffi, V., Hallman, E.~J., et al.\ 2014, arXiv:1407.1783
\bibitem[Zwicky(1937)]{zwi37} Zwicky, F.\ 1937, \apj, 86, 217
\end{thebibliography}{}

>>>>

We seek to address these issues by releasing the ``Galaxy Cluster Merger Catalog'', an extensive suite of mock observations and related data for simulations of galaxy cluster mergers.

The goal of the catalog is to provide a way to connect simulations of galaxy cluster mergers
with multiwavelength observations of real merging clusters. Producing simulation data in terms of
observed quantities at many different epochs and from many different lines of sight provides an
opportunity for observers to compare clusters in their observations with a particular merging
scenario. The data here may also be analyzed in its own right, to make predictions for what various investigations of real clusters may reveal.

@@

At the time of writing, the catalog contains data products from idealized binary cluster merger
simulations. In the future, the catalog will include data products from a variety of galaxy cluster merger and related galaxy cluster simulations, including those from cosmological simulations and simulations of interactions between clusters and their member galaxies. The types of data products are likely to expand and diversify with the inclusion of new simulations.

The galaxy cluster merger simulation data in the catalog comes from state-of-the-art N-body and hydrodynamics codes such as FLASH and Athena. The exact physics and algorithms employed by the simulations vary, but in general:

\begin{itemize}
\item Each simulation is simulated using an adaptive or static mesh refinement (AMR/SMR) grid \citep{ber89} with varying resolution throughout the domain, with refinement occuring on criteria such as sharp jumps in density and temperature, matter density, and selected regions such as the cluster center. Eventually, the catalog will include particle-based simulations as well.
\item The equations of hydrodynamics (HD) or magnetohydrodynamics (MHD) are modeled using a conservative finite-volume scheme, employing Riemann solvers for evolving the flux of physical quantities and using high-order reconstruction schemes such as the Piecewise-Parabolic Method \citep[PPM,][]{col84}. Magnetic fields are evolved such that the condition $\nabla \cdot {\bf B} = 0$ is met, typically by a constrained transport scheme \citep[CT][]{eva88}. Eventually, the catalog will include simulations peformed with smoothed particle hydrodynamics.
\item Each simulation assumes an ideal gas law equation of state with $\gamma = 5/3$ and primordial abundances of H/He with trace amounts of metals, yielding a mean molecular weight of $\mu = 0.6$.
\item If dark matter is included, it is modeled by an N-body solver for a collection of collisionless massive particles, which interact with the gas component only via gravity.
\item The gravity in the simulations is either modeled as a rigid gravitational potential associated with each cluster or by computing the self-gravity of the gas and dark matter using a Poisson solver \citep[e.g.,][]{ric08}.
\item Depending on the goals of the simulation study, other physics, such as viscosity, thermal conduction, radiative cooling, etc., may be included.
\end{itemize}

@@

The data products are all written in the FITS format \citep{pen10}, in image and table form. Each FITS file may contain more than one image or table extension. The header of each extension contains coordinate information stored using the standard World Coordinate System \citep[WCS,][]{gre02, cal02} keywords. Each FITS file contains one or both of the following two coordinate systems:

@@

\begin{thebibliography}{}
\bibitem[Berger \& Colella(1989)]{ber89} Berger, M.~J., \& Colella, P.\ 1989, Journal of Computational Physics, 82, 64
\bibitem[Br{\"u}ggen et al.(2012)]{bru12} Br{\"u}ggen, M., Bykov, A., Ryu, D., R{\"o}ttgering, H.\ 2012, \ssr, 166, 187
\bibitem[Brunetti \& Lazarian(2007)]{bru07} Brunetti, G., \& Lazarian, A.\ 2007, \mnras, 378, 245
\bibitem[Colella \& Woodward(1984)]{col84} Colella, P., \& Woodward, P.~R.\ 1984, Journal of Computational Physics, 54, 174
\bibitem[Greisen \& Calabretta(2002)]{gre02} Greisen, E.~W., \& Calabretta, M.~R.\ 2002, \aap, 395, 1061
\bibitem[Calabretta \& Greisen(2002)]{cal02} Calabretta, M.~R., \& Greisen, E.~W.\ 2002, \aap, 395, 1077
\bibitem[Clowe et al.(2004)]{clo04} Clowe, D., Gonzalez, A., \& Markevitch, M.\ 2004, \apj, 604, 596
\bibitem[Chluba et al.(2012)]{chl12} Chluba, J., Nagai, D., Sazonov, S., \& Nelson, K.\ 2012, \mnras, 426, 510
\bibitem[Chluba et al.(2013)]{chl13} Chluba, J., Switzer, E., Nelson, K., \& Nagai, D.\ 2013, \mnras, 430, 3054
\bibitem[Donnert et al.(2013)]{don13} Donnert, J., Dolag, K., Brunetti, G., \& Cassano, R.\ 2013, \mnras, 429, 3564
\bibitem[Evans \& Hawley(1988)]{eva88} Evans, C.~R., \& Hawley, J.~F.\ 1988, \apj, 332, 659
\bibitem[Feretti(2005)]{fer05} Feretti, L.\ 2005, Advances in Space Research, 36, 729
\bibitem[Ford et al.(2014)]{for14} Ford, J., Hildebrandt, H., Van Waerbeke, L., et al.\ 2014, \mnras, 439, 3755
\bibitem[Forman et al.(1972)]{for72} Forman, W., Kellogg, E., Gursky, H., Tananbaum, H., \& Giacconi, R.\ 1972, \apj, 178, 309
\bibitem[Markevitch et al.(2004)]{mar04} Markevitch, M., Gonzalez, A.~H., Clowe, D., et al.\ 2004, \apj, 606, 819
\bibitem[Pence et al.(2010)]{pen10} Pence, W.~D., Chiappetti, L., Page, C.~G., Shaw, R.~A., \& Stobie, E.\ 2010, \aap, 524, A42
\bibitem[Poole et al.(2006)]{poo06} Poole, G.~B., Fardal, M.~A., Babul, A., McCarthy, I.~G., Quinn, T., \& Wadsley, J.\ 2006, \mnras, 373, 881
\bibitem[Ricker \& Sarazin(2001)]{ric01} Ricker, P.~M., \& Sarazin, C.~L.\ 2001, \apj, 561, 621
\bibitem[Ricker(2008)]{ric08} Ricker, P.~M.\ 2008, \apjs, 176, 293-300
\bibitem[Skillman et al.(2013)]{ski13} Skillman, S.~W., Xu, H., Hallman, E.~J., et al.\ 2013, \apj, 765, 21
\bibitem[Sunyaev \& Zeldovich(1972)]{sun72} Sunyaev, R.~A., \& Zeldovich, Y.~B.\ 1972, Comments on Astrophysics and Space Physics, 4, 173
\bibitem[Turk et al.(2011)]{tur11} Turk, M.~J., Smith, B.~D., Oishi, J.~S., Skory, S., Skillman, S.~W., Abel, T., \& Norman, M.~L.\ 2011, \apjs, 192, 9
\bibitem[van Weeren et al.(2010)]{vwe10} van Weeren, R.~J., R{\"o}ttgering, H.~J.~A., Br{\"u}ggen, M., \& Hoeft, M.\ 2010, Science, 330, 347
\bibitem[Vazza et al.(2009)]{vaz09} Vazza, F., Brunetti, G., Kritsuk, A., et al.\ 2009, \aap, 504, 33
\bibitem[Yu et al.(2015)]{yu15} Yu, L., Nelson, K., \& Nagai, D.\ 2015, \apj, 807, 12
\bibitem[ZuHone et al.(2010)]{zuh10} ZuHone, J.~A., Markevitch, M., \& Johnson, R.~E.\ 2010, \apj, 717, 908 (ZMJ10)
\bibitem[ZuHone(2011)]{zuh11} ZuHone, J.~A.\ 2011, \apj, 728, 54 (Z11)
\bibitem[ZuHone et al.(2014)]{zuh14} ZuHone, J.~A., Biffi, V., Hallman, E.~J., et al.\ 2014, arXiv:1407.1783
\bibitem[Zwicky(1937)]{zwi37} Zwicky, F.\ 1937, \apj, 86, 217
\end{thebibliography}{}
